Data Management for LSST Special Programs

### 2023-10-16 sec_intro.tex
minor updates

The three memoranda for Rubin Data Management regarding Special Programs are:
\begin{enumerate}
\item All visits should have both a region and a program label.
These labels should be propagated to all derived data products
(e.g., processed images, catalog data, and alerts; Section~\ref{ssec:sci_labels}).
\item All visits that \emph{can} be processed by the Prompt pipelines and generate 
alerts \emph{should} be, in support of time domain and Solar System science goals (Section~\ref{ssec:proc_wfd}).
\item Special Processing to create ``unique and separate" data products for Special Programs
should be done when it is possible and necessary, as defined in Section~\ref{ssec:proc_rdm}. 
\end{enumerate}

@@

\subsubsection{Wide Fast Deep (WFD) Main Survey}

The WFD program is the core science program of the LSST, designed to achieve the science 
goals defined by the Science Requirements Document (SRD; \citeds{LPM-17}).

The WFD is defined from a scheduling perspective as a certain cadence and filter balance 
(i.e., an observing strategy; a program) 
that covers the low-dust region (extragalactic areas) and several special regions:
the Galactic bulge and plane; the South Celestial Pole (SCP); the North Ecliptic Spur (NES);
and the Virgo Cluster \citedsp{PSTN-055}.

The WFD's regions will compose a contiguous sky footprint that covers at least $\sim$18000 deg$^2$ with 
$\gtrsim$800 visits per field, expected to be accomplished with 85--90\% 
of the observing time.

The WFD is expected to use alternative standard visits in the $u$-band and 
standard visits in all other bands \citedsp{PSTN-055}.
Rolling cadence is expected to be implemented in the low-dust region only.

>>>>

\subsection{Takeaways for Rubin Data Management}

The three memoranda for Rubin Data Management regarding Special Programs are:
\begin{enumerate}
\item All visits should have both a region and a program label.
These labels should be propagated to all derived data products, such as
processed images, catalog data, and alerts. (Section~\ref{ssec:sci_labels})
\item All visits that \emph{can} be processed by the Prompt pipelines and generate 
alerts \emph{should} be, in support of time domain and Solar System science goals. (Section~\ref{ssec:proc_wfd})
\item Special Processing to create ``unique and separate" data products for Special Programs
should be done when it is possible and necessary, as defined in Section~\ref{ssec:proc_rdm}.
\end{enumerate}

@@

\subsubsection{Wide Fast Deep (WFD) Program}

The WFD is the core science program of the LSST, designed to achieve the science 
goals defined by the Science Requirements Document (SRD; \citeds{LPM-17}).

The WFD program is defined from a scheduling perspective as a certain observing strategy
(i.e., a set of cadences and filter balances) applied to the low-dust region 
(extragalactic areas) and several special regions:
the Galactic bulge and plane; the South Celestial Pole (SCP); the North Ecliptic Spur (NES);
and the Virgo Cluster \citedsp{PSTN-055}.

The WFD's regions will compose a contiguous sky footprint that covers at 
least $\sim$18000 deg$^2$ with $\gtrsim$800 visits per field, 
and is expected to be accomplished with 85--90\% of the observing time.

The WFD is expected to use alternative standard visits in the $u$-band and 
standard visits in all other bands \citedsp{PSTN-055}.
Different cadences, filter balances, rotational dithers, etc., might
be applied in the different regions composing WFD.
For example, rolling cadence is expected to be implemented in the low-dust region only.
WFD program data will be processed with regular (non-special) processing.
